---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

The paper by Wilson et. al. describe, among other things, that providing the exact code (with dependencies and documentation) as well as version control can greatly improve computational reproducibility. This allows researchers to simply upload their code repository to a place like github, where other researchers can easily clone it and run the same scripts to reproduce the results of the paper (this is fairly common nowadays in my field). A tool like R, but of course any other programming language, in combination with git can therefore assist with computational reproducibility, especially as it is open-source and widely used in the scientific community, which facilitates the process of reproducing computational work.


3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
sqrt(4^13)
```


4) Push this homework to the GitHub repository for the homework. 





